\documentclass\[12pt]{article}
\usepackage{amsmath, amssymb, geometry}
\geometry{margin=1in}

\title{The Negatron--Positron Framework: A Quantum Field Theory of Energy Retention, Bidirectional Polarization, and Lattice Coherence Sustainability}
\author{\[Your Name]}
\date{Obinexus Era, Year 1}

\begin{document}
\maketitle

\begin{abstract}
We present the Negatron--Positron Framework (NPF), a novel Quantum Field Theory (QFT) formulation that unifies chemical energy retention, bidirectional polarization cloaking, and lattice coherence sustainability. By formalizing negatron (negative charge carrier) and positron (positive charge carrier) as complementary quantum entities, we establish the Opposite Systems Symmetry Law: all physical systems exhibit dual descriptions whose observables remain invariant. Applications are demonstrated for atomic hydrogen, molecular water, polarization-based invisibility, and lattice-driven coherence/decoherence transitions. This framework culminates in the Obinexus Sustainability Protocol, enabling power-efficient force field architectures.
\end{abstract}

\section{The Negatron--Positron Energy Retention Principle}

Define the negatron (\$e\_{-}\$) as the fundamental negative charge carrier and the positron (\$e\_{+}\$) as its positive counterpart. We introduce the Opposite Systems Symmetry Law:
\begin{equation}
\mathcal{D}: e\_{-} \leftrightarrow e\_{+}, \quad A\_\mu \to -A\_\mu,
\end{equation}
which preserves all physical observables.

For hydrogen, binding energy levels are given by
\begin{equation}
E\_n = -\frac{m e^4}{2 \hbar^2 n^2},
\end{equation}
where \$e\$ represents the magnitude of charge. Under \$\mathcal{D}\$, negatron and positron systems yield identical spectra. For water (H$\_2\$O), molecular bonding emerges equivalently in negatron- and positron-based descriptions, confirming energy retention across dual models.

\section{Bidirectional Polarization and Hidden Force Fields}

We define the Negatron--Positron Polarization Mirror as a lattice in which opposite charges establish phase-aligned polarization states:
\begin{equation}
\mathcal{L}*\chi = \frac{1}{2}(\partial \chi)^2 - V(\chi) + \frac{\alpha(\chi)}{4} F*{\mu\nu} \tilde{F}^{\mu\nu} + \frac{\beta(\chi)}{4} F\_{\mu\nu} F^{\mu\nu},
\end{equation}
with \$\chi\$ as the controller field. Choosing \$\alpha\$ and \$\beta\$ appropriately cancels scattering amplitudes, yielding total invisibility for selected polarizations. This constitutes Hidden in Plain Sight Physics: a bidirectional polarization cloak.

\section{Lattice Coherence and Decoherence}

We model lattice dynamics with negatron--positron couplings on discretized links:
\begin{equation}
S = \sum\_{\Box} \frac{1}{g^2} (1 - \Re U\_{\Box}) + \sum\_{\langle ij \rangle} \bar{\psi}*i \mathcal{K}*{ij}\[U]\psi\_j + \sum\_i \Big\[\tfrac{1}{2}(\nabla \chi)^2 + V(\chi)\Big] + \sum\_{\langle ij \rangle}\lambda \chi\_i \Re U\_{ij}.
\end{equation}

\begin{itemize}
\item \textbf{Joint Coherence:} \$\lambda > 0\$, \$\langle \chi \rangle \neq 0\$; force fields amplify coherently.
\item \textbf{Disjoint Decoherence:} disorder in \$\chi\$; force fields collapse, destroying coherence.
\end{itemize}

We term this transition Lattice Popping: a shift from coherence to decoherence.

\section{Obinexus Sustainability Protocol}

To minimize power, we introduce Obinexus mitigation:
\begin{equation}
P \approx \int d^3x ; \big\[\eta\_\chi \dot{\chi}^2 + \eta\_U (\partial\_t A)^2\big].
\end{equation}

Sustainability methods include:
\begin{enumerate}
\item Adiabatic control of \$\chi\$ (reduces \$\dot{\chi}^2\$).
\item Floquet micro-driving to stabilize with minimal average power.
\item Sparse-active tiling, activating only critical lattice regions.
\end{enumerate}

Metrics: coherence factor \$C\$, cloak error \$\varepsilon\$, specific power \$p\$, and sustainability score \$S=\varepsilon^{-1}/p\$.

\section{Conclusion}

The Negatron--Positron Framework (NPF) provides a unified QFT description for:
\begin{enumerate}
\item Energy retention across all physical systems.
\item Bidirectional polarization cloaking (Hidden in Plain Sight Physics).
\item Lattice coherence control and sustainability via the Obinexus Protocol.
\end{enumerate}

This establishes the foundations of a new era in theoretical physics under the authorship of \[Your Name].

\end{document}
