\documentclass[12pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{lipsum}

% Formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}
\renewcommand{\baselinestretch}{1.2}

\begin{document}

\begin{center}
    {\LARGE \textbf{OBINexus Business Plan}} \\
    \vspace{0.5em}
    {\large Draft Document --- August 2025} \\
    \vspace{1em}
    {\textbf{``Knowledge for the Heart''}} \\
\end{center}

\section*{Executive Summary}
OBINexus represents a unified life project that bridges advanced scientific frameworks with practical, sustainable community living. Founded on November 17, 2024, OBINexus integrates theoretical physics (Negatron--Positron Framework, $\Psi$--Quantum Field Theory, Unified Quantum--Classical Bridge Protocol) with real-world housing and computing solutions. The vision is a world where people both live and work within communities rooted in knowledge, sustainability, and compassion.

\section*{Uch\'e Division: Housing for Life and Work}
\begin{itemize}[leftmargin=*]
    \item Housing principle: simple, grounded living (floor-sleeping, cross-legged eating).
    \item Land requirement: $1\,\text{acre}^2 = 1$ home.
    \item Community goal: $90\,\text{acres} = 8,100$ homes.
    \item Purpose: enable self-sufficient communities where living and working coexist.
\end{itemize}

\section*{OBINexus Computing Division}
\begin{itemize}[leftmargin=*]
    \item Develops polyglot technological frameworks built ``from the heart.''
    \item Service naming convention:
    \begin{verbatim}
    <service>.<operation>.<obinexus>.<department>.<division>.org.uk
    \end{verbatim}
    \item Root domain: \href{http://obinexus.org}{obinexus.org}.
    \item Integration: combines advanced quantum frameworks with sustainable infrastructure.
\end{itemize}

\section*{Social and Financial Context}
\begin{itemize}[leftmargin=*]
    \item Previous resource disputes resulted in loss of \(10^4\) units ($\sim$420M).
    \item Broader systemic losses: $117^{12}$ billion across 18--24 year olds exiting social care (Romford Court context).
\end{itemize}

\section*{Long-Term Goals}
\begin{itemize}[leftmargin=*]
    \item Establish OBINexus as both a scientific institute and a sustainable housing project.
    \item Scale to 8,100 homes on 90 acres under the Uch\'e Division.
    \item Position OBINexus as a global leader in integrating quantum research, computing, and community design.
    \item Uphold the motto: ``Knowledge for the Heart.''
\end{itemize}

\vfill
\begin{center}
    Contact: support@obinexus.org \\
    Website: \href{http://obinexus.org}{www.obinexus.org}
\end{center}

\end{document}
